Template for indicator documentation

### 2023-09-12 functional_plant_indicators_wetland.Rmd
fix FPI_wetland bug

# summarizing the indicator scores
res.wetland %>%
  group_by(fp_ind) %>%
  dplyr::summarize(Mean = mean(scaled_value, na.rm=TRUE), SD = sd(scaled_value, na.rm=TRUE), N = length(scaled_value))

>>>>

# add original values as well
res.wetland <-
res.wetland %>% add_column(original = results.wetland[['original']] %>%
pivot_longer(
cols = c("Light1","Light2","Moist1","Moist2","pH1","pH2","Nitrogen1","Nitrogen2"),
names_to = NULL,
values_to = "original",
values_drop_na = FALSE
) %>%
pull(original)
)
